{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Slight wording changes for Fourier basis

	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(t)$ for prediction or inference. \\

@@

	\paragraph{Fourier Basis}
	Fourier series decomposes a periodic function with a weighted sum of trigonometric functions. Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between $0$ and $1$, and we can then apply the Fourier series to approximate the function for smoothing. As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions. That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.

@@

	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
	 \end{equation}

>>>>

	 Here, $X(\omega)$ is a random function, $Y(\omega)$ is the response variable and $\beta(s)$ the coefficient function. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional. As in the framework of scalar linear regression, estimating $\beta(t)$ is particularly interesting for prediction or inference. \\

@@

	\paragraph{Fourier Basis}
	In the same way the monomial basis corresponds to the Taylor expansion, the Fourier basis corresponds to the Fourier series. The Fourier series can be used to decompose a periodic function into a weighted sum of trigonometric functions. Equation \ref{Fourier_Series} shows an example for a periodic function $s(x)$ defined on the interval $[0,1]$.

	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_n \cos(2\pi n x - \phi_n) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_n \cos(2\pi n x) + b_n \sin(2\pi n x)\right]
	\end{equation}

	In its classical form, the series is represented in the so called amplitude-phase form. This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift. Therefore, rewriting the series in the sine-cosine form through a simple trigonometry formula as shown above is necessary. Due to this origin of the Fourier basis it is reasonable to restrict the number of Fourier basis functions to odd numbered values.
	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.

	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

	Therefore, its elements inherit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, generally resulting in uniformly smooth expansions.

@@

	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
	 \end{equation}
